Tracing the Stellar Halos of Massive Galaxies to 100 kpc at $0.3<z<0.5$ using Hyper Suprime-Cam

### 2017-06-30 draft/paper1_rachel.tex
Edit stellar mass measurement 4

    With the help of the \texttt{S82-MGC} (\citealt{Bundy2015}), we investigate the 
    \mstar{} completeness of our samples. 
    The \texttt{S82-MGC} sample matches the deeper SDSS photometric data in the 
    Stripe 82 region (\citealt{Annis2014}) with the near infrared data from the United 
    Kingdom Infrared Telescope Infrared Deep Sky Survey (UKIDSS; 
    \citealt{Lawrence2007}). 
    The deeper photometry and better photo-$z$s \rachel{Are `deeper' and `brighter' here compared to SDSS?  It isn't deeper than HSC, is it?  Should be clear what we are comparing here.} make the \texttt{S82-MGC} sample 
    complete to \logms{}$\geq 11.2$ at $z<0.7$ which makes it sufficient to evaluate 
    the completeness of our HSC sample.   
	By comparing with the Stripe 82 Massive Galaxy Catalog
    (\texttt{S82-MGC}; \citealt{Bundy2015}), \citet{Leauthaud2016} have measured the
    \mstar{} completeness of the combined BOSS and SDSS samples. 
    They estimate that the BOSS spec-$z$ sample, which is the main source of redshifts for our sample, is about 80\% complete at 
    \logms{}$\geq 11.6$ at $0.3 < z < 0.5$. The GAMA survey is 80\% complete down to 
    $10^{10.8}$\msun at $z{\sim} 0.3$, but is only 80\% complete to 
    $10^{12.0}$\msun{} at $z{\sim} 0.5$ according to \citet{Taylor2011} (e.g.\ 
    their Fig.~6).

    There are 20453 \texttt{S82-MGC} galaxies that are also in the \texttt{hscPho} 
    sample at $0.3 \leq z_{\mathrm{s82}} \leq 0.5$.  Because the \texttt{S82-MGC} uses  cmodel  magnitudes,  in this section we use  \mcmodel{} for consistency with the  \texttt{S82-MGC} catalog.  The \texttt{S82-MGC} also uses \texttt{iSEDFit} with similar assumptions as used in this work and we find excellent agreement between HSC  \mcmodel{} and the mass derived in  the \texttt{S82-MGC} which includes NIR data from UKIDSS;

    Figure~\ref{fig:mass_complete} compares the number density distributions of galaxies from \texttt{S82-MGC} with those from our sample\footnote{We do not apply any statistical corrections for completeness and hence we do not use the term ``stellar mass function'' to avoid confusion;
    Errors on the distributions are estimated via bootstrap resampling.}. 
    Based on Fig.~\ref{fig:mass_complete}, we conclude that our sample of massive 
    galaxies is reasonably complete down to \logmcmodel{}${\sim} 11.5$ at 
    $0.3 \leq z \leq 0.5$. 
    %The \rbcg{} sample is less affected by completeness because we can utilize 
    %photo-$z$s from \redm{}. 
    %However, the completeness of the \nbcg{} sample is still limited by the 
    %availability of spec-$z$s from BOSS.    
    Given the average difference between \mtot{} and \mcmodel{}, we will focus on galaxies with \logmtot{}$> 11.6$ where our sample shows good completeness. In our discussion section, we will also show results for massive galaxies with $11.4 \le$\logmtot{}$<11.6$ but we caution that our sample is incomplete in this  lower mass bin.
\rachel{I am a bit lost as to the primary source of this incompleteness.  Is it due to limitations inherited from CMASS, or something inherent to the data (no NIR) or procedure used to select the galaxies in this work?}

>>>>

    With the help of the \texttt{S82-MGC} (\citealt{Bundy2015}), we investigate the 
    \mstar{} completeness of our samples. 
    The \texttt{S82-MGC} sample matches the deeper SDSS photometric data in the 
    Stripe 82 region (\citealt{Annis2014}) with the near infrared data from the United 
    Kingdom Infrared Telescope Infrared Deep Sky Survey (UKIDSS; 
    \citealt{Lawrence2007}). 
    Comparing to normal SDSS images, the deeper photometry and better photo-$z$s 
    from \texttt{S82-MGC} make this sample complete to \logms{}$\geq 11.2$ at $z<0.7$ 
    which makes it sufficient to evaluate the completeness of our HSC sample.   
	By comparing with the Stripe 82 Massive Galaxy Catalog
    (\texttt{S82-MGC}; \citealt{Bundy2015}), \citet{Leauthaud2016} have measured the
    \mstar{} completeness of the combined BOSS and SDSS samples. 
    They estimate that the BOSS spec-$z$ sample, which is the main source of redshifts 
    for our sample, is about 80\% complete at 
    \logms{}$\geq 11.6$ at $0.3 < z < 0.5$. The GAMA survey is 80\% complete down to 
    $10^{10.8}$\msun at $z{\sim} 0.3$, but is only 80\% complete to 
    $10^{12.0}$\msun{} at $z{\sim} 0.5$ according to \citet{Taylor2011} (e.g.\ 
    their Fig.~6).

    There are 20453 \texttt{S82-MGC} galaxies that are also in the \texttt{hscPho} 
    sample at $0.3 \leq z_{\mathrm{s82}} \leq 0.5$.  
    Because the \texttt{S82-MGC} uses \cmodel{} magnitudes, in this section we use  
    \mcmodel{} for consistency with the \texttt{S82-MGC} catalog.  
    The \texttt{S82-MGC} also uses \texttt{iSEDFit} with similar assumptions as 
    used in this work and we find excellent agreement between HSC \mcmodel{} and 
    the mass derived by \texttt{S82-MGC} which includes NIR data from UKIDSS;

    Figure~\ref{fig:mass_complete} compares the number density distributions of 
    galaxies from \texttt{S82-MGC} with those from our sample\footnote{We do not 
    apply any statistical corrections for completeness and hence we do not use the 
    term ``stellar mass function'' to avoid confusion;
    Errors on the distributions are estimated via bootstrap resampling.}. 
    Based on Fig.~\ref{fig:mass_complete}, we conclude that our sample of massive 
    galaxies is reasonably complete down to \logmcmodel{}${\sim} 11.5$ at 
    $0.3 \leq z \leq 0.5$. 
    %The \rbcg{} sample is less affected by completeness because we can utilize 
    %photo-$z$s from \redm{}. 
    %However, the completeness of the \nbcg{} sample is still limited by the 
    %availability of spec-$z$s from BOSS.    
    Given the average difference between \mtot{} and \mcmodel{}, we will focus on 
    galaxies with \logmtot{}$> 11.6$ where our sample shows good completeness. 
    In our discussion section, we will also show results for massive galaxies 
    with $11.4 \le$\logmtot{}$<11.6$ but we caution that our sample is incomplete 
    in this lower mass bin mainly due to the intrinsic incompleteness of the 
    SDSS/BOSS spec-$z$ (see \citealt{Leauthaud2016}).
